GMU MS SWE Handbook\\{\large A Handbook For the Masters of Software Engineering program at George Mason University

### 2024-10-15 ennv.tex
update

>>>>

\paragraph{Feed-Forward Network} A Feed-Forward Network (FFN) is a type of neural network where the connections between the neurons do not form a cycle. In an FFN, the information flows in one direction, from the input layer to the output layer. FFNs are the simplest type of neural network and are often used in classification and regression tasks.  A fully connected feed-forward neural network (FNN) is a type of FFN where every neuron in a layer is connected to every neuron in the next layer.
\begin{center}
\begin{tikzpicture}[scale=0.8, transform shape]
% Input Layer
\node at (0,4) {\textbf{Input Layer}};
\foreach \x in {1,2,3,4} {
    \node[circle, draw=black, fill=white, minimum size=0.6cm] (I\x) at (0,4-\x) {};
}

% Hidden Layer 1
\node at (3,4) {\textbf{Hidden Layer 1}};
\foreach \x in {1,2,3,4,5} {
    \node[circle, draw=black, fill=white, minimum size=0.6cm] (H1\x) at (3,4.5-\x) {};
}

% Hidden Layer 2
\node at (6,4) {\textbf{Hidden Layer 2}};
\foreach \x in {1,2,3,4,5} {
    \node[circle, draw=black, fill=white, minimum size=0.6cm] (H2\x) at (6,4.5-\x) {};
}

% Output Layer
\node at (9,3.5) {\textbf{Output Layer}};
\foreach \x in {1,2,3} {
    \node[circle, draw=black, fill=white, minimum size=0.6cm] (O\x) at (9,3.5-\x) {};
}

% Connections
\foreach \i in {1,2,3,4}
    \foreach \j in {1,2,3,4,5}
        \draw[->] (I\i) -- (H1\j);

\foreach \i in {1,2,3,4,5}
    \foreach \j in {1,2,3,4,5}
        \draw[->] (H1\i) -- (H2\j);

\foreach \i in {1,2,3,4,5}
    \foreach \j in {1,2,3}
        \draw[->] (H2\i) -- (O\j);

\end{tikzpicture}
\end{center}
